# Data Visualization for Stock with R

**R** is a very powerful language and it is widely used in statistics and finance domain. For applied finance using R, please check web site ["R/Finance conference for applied finance using R"](http://www.rinfinance.com/)

I want to show how easily to use R to draw stock charts in this blog. Let's take DDD as an example. 

```{r cache=FALSE, echo=FALSE, message=FALSE, include=FALSE}
# let's load quantmod library and get symbol DDD
library(quantmod)
getSymbols("DDD")
```

## Summary and Chart

```{r fig.width=7, fig.height=6}
summary(DDD)
candleChart(last(DDD, "3 months"), theme="white", TA = NULL)
```

## Functions

I want to add the average price on the privous chart. I will set daily average price be approximated by  
$$
P_i = (C_i + H_i + L_i) / 3
$$

```{r}
avgP = function(symbol) {
   apply(HLC(symbol), 1, mean)  
}
last(avgP(DDD), "10 days")
addAvgP = newTA(FUN=avgP, col = 1, legend  ="AvgPrice")
addAvgP(on = 1)
```

Let $V_i$ be the percentag variations of today's close to the following $k$ days average prices. It is very easy to generate a table in R to achieve the goal.

```{r}
vtable = function(symbol, margin = 0.05,  days = 5) {
  p = avgP(symbol)
  # initialize NA matrix
  r = matrix(NA, ncol = days, nrow = NROW(symbol))
  # calculate Vi
  for (x in 1:days) r[, x] = Next(Delt(p, k=x ), x)
  v = apply(r[1: (NROW(r) - days),], 1, function(y) sum(y[y> margin | x < -margin]))
  v
}

last(vtable(DDD),10)
```


